Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-11-06 boutiquespaper.tex

\paragraph{GinFizz}
We integrated the
GinFizz\footnote{\url{https://github.com/thomashirsch/ginfizz}}
Nipype-based fMRI pre-processing pipeline in VIP with \boutiques. \todo{Sorina, Pascal, a few lines on the technical deployment?}
%% Ginfizz performs multiple
%% preprocessing steps and basic analyses such as: (i) realignment
%% (motion registration and correction), (ii) slice timing (temporal
%% interpolation to correct for the delay of acquisition between slices),
%% (iii) coregistration (registering functional and structural data),
%% (iv) normalization (registering of functional and anatomical data to a
%% match a template that has to be specified), and (iv) smoothing
%% (spatial filtering to increase Signal to Noise ratio).

@@

\paragraph{CreaPhase}
A phase contrast simulator called CreaPhase, developed at Creatis, was
integrated in VIP through \boutiques. The CreaPhase inputs had
certain particularities (some nedeed to be enclosed in simple quotes,
other were vectors of variable size enclosed in brackets) that
required the post-processing of the wrapper script generated by the
Boutiques importer. \todo{Sorina: reference?}

>>>>

\paragraph{GinFizz}
We integrated the
GinFizz\footnote{\url{https://github.com/thomashirsch/ginfizz}}
Nipype-based fMRI pre-processing pipeline in VIP with \boutiques. 
A few technical issues were encountered with the Docker container. 
They were mainly due to the re-use of multiple containers build 
with specific users, leading to file access issues. We therefore 
had to override the permissions on the files and folders necessary
to the correct execution of the GinFizz application.

%% Ginfizz performs multiple
%% preprocessing steps and basic analyses such as: (i) realignment
%% (motion registration and correction), (ii) slice timing (temporal
%% interpolation to correct for the delay of acquisition between slices),
%% (iii) coregistration (registering functional and structural data),
%% (iv) normalization (registering of functional and anatomical data to a
%% match a template that has to be specified), and (iv) smoothing
%% (spatial filtering to increase Signal to Noise ratio).

@@

\paragraph{CreaPhase}
A phase contrast simulator called CreaPhase\cite{WEBE-17}, developed at Creatis, was
integrated in VIP through \boutiques. The CreaPhase inputs had
certain particularities (some nedeed to be enclosed in simple quotes,
other were vectors of variable size enclosed in brackets) that
required the post-processing of the wrapper script generated by the
Boutiques importer.
